A Tale of Two Transects

### 2020-02-12 writing/transect_paper.Rmd
move heattree code to light plan

```{r ecm-heattree, fig.cap = "(ref:ecm-heattree)"}
taxdata2 <- readd(taxdata_ECM)

val_cols <- names(taxdata2$data$tax_read) %>%
    keep(str_detect, "reads_.+_.+_Unite_.+")

taxdata2$filter_obs(
  "tax_read",
  rowSums(select_at(taxdata2$data$tax_read, val_cols)) > 0,
  drop_taxa = TRUE,
  drop_obs = TRUE,
  supertaxa = TRUE,
  reassign_obs = FALSE) %>%
  invisible()

taxdata2$data$diff_read <- metacoder::compare_groups(
  taxdata2,
  data = "tax_read",
  cols = val_cols,
  groups = val_cols %>%
    str_replace("reads_.+_(.+)_Unite_.+", "\\1"),
  func = function(abund1, abund2) {
    list(read_ratio = log10(mean(abund1) / mean(abund2)))
  }
)
taxdata2$data$diff_asv <- metacoder::compare_groups(
  taxdata2,
  data = "tax_asv",
  cols = names(taxdata2$data$tax_asv) %>% keep(startsWith, "ASVs_"),
  groups = names(taxdata2$data$tax_asv) %>%
    keep(startsWith, "ASVs_") %>%
    str_replace("ASVs_.+_(.+)_.+_.+", "\\1"),
  func = function(abund1, abund2) {
    list(ASV_ratio = log10(mean(abund1) / mean(abund2)))
  }
)

taxdata2 <- taxdata2$filter_taxa(!is.nan(ASV_ratio), !is.nan(read_ratio))

set.seed(3)
oldtheme <- theme_update(panel.border = element_blank())
taxdata2 %>%
  metacoder::heat_tree(
    layout = "davidson-harel",
    initial_layout = "reingold-tilford",

    node_color = read_ratio,
    node_color_range = metacoder::diverging_palette(),
    node_color_trans = "linear",
    node_color_axis_label = "Read abundance ratio",
    node_color_interval = c(-3, 3),

    edge_color = ASV_ratio,
    edge_color_range = metacoder::diverging_palette(),
    edge_color_trans = "linear",
    edge_color_axis_label = "ASV count ratio",
    edge_color_interval = c(-0.75, 0.75),

    node_label = taxon_names,
    node_label_size_range = c(0.02, 0.03),
    # title = unique(paste(.$data$diff_read$treatment_1, "vs.", .$data$diff_read$treatment_2)),
    aspect_ratio = 3/2
  )
theme_set(oldtheme)
```

>>>>

```{r ecm-heattree, fig.cap = "(ref:ecm-heattree)"}
oldtheme <- theme_update(panel.border = element_blank())
readd(ecm_heattree)
theme_set(oldtheme)
```
